### 2021-08-01 paper/paper.tex
update MPI TODO note
more positive aspects of julia

  \item High-order discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

Abstractions such as (variants of) the \lstinline{solver}, the \lstinline{mesh},
and the \lstinline{equations} are based on a common interface. Using multiple
dispatch in Julia, internal implementations are specialized accordingly. For
example, changing the volume terms of the DG discretization from the standard
weak form to entropy stable and/or shock capturing methods can be achieved by
passing one additional parameter to the \lstinline{DGSEM} constructor in the
example above.

@@

@@

@@

\todo{TODO: Michael, could you please write something here? You are much more
experienced with MPI and HPC} %TODO Michael

>>>>

  \item High-order matrix-free discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

Abstractions such as (variants of) the \lstinline{solver}, the \lstinline{mesh},
and the \lstinline{equations} are based on a common interface. Using multiple
dispatch in Julia, internal implementations are specialized accordingly. For
example, changing the volume terms of the DG discretization from the standard
weak form to entropy stable and/or shock capturing methods can be achieved by
passing one additional parameter to the \lstinline{DGSEM} constructor in the
example above. Moreover, there is no hidden global state and multiple instances
of similar structures can be instantiated simultaneously. In particular, multiple
semidiscretizations (in possibly different spatial dimensions) can be created
and used in the same code.

@@

Julia itself and most packages are developed on GitHub. The community provides
a lot of tools for using corresponding CI setups, preparing and publishing
documentation\footnote{\url{https://github.com/JuliaDocs/Documenter.jl}},
and related tasks. This setup also encourages other good software development
practices that we use in \trixi such as mandatory code review before pull requests
are merged.

@@

\subsubsection{Julia is free}

Julia itself is released under the MIT license and ships some GPL-licensed
third-party software (that can optionally be disabled for commercial purposes).
Many packages in the Julia ecosystem follow this approach and are freely available
under the permissive MIT license, including \trixi. This allows using Julia
without needing to pay for commercial software. In particular, students can
work with the software on their private computers without restrictions.

@@

\todo{TODO: Michael, could you please write something here? You are much more
experienced with MPI and HPC. Be aware of \cite{omlin2020solving} to not step
on anybodies toes...} %TODO Michael
